---
title: "Jan 30 2018"
author: "Felicia Zhang"
date: '2018-01-30'
output: html_document
---

Recreating graphs for VSL paper
Making sure graphs are consistent with labels, colors
```{r setup, include=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)
library(tidyr)

#1. load data (master)
OmixOrig = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges_Mix/Data/OMix.rds")
OV1Orig = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/OrangesV1.rds") 
OV2Orig = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/OrangesV2/Data/OrangesV2.rds")
Omix.Trip = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges_Mix/Data/Omix_trip_zscore.rds")
Omix.Rand = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges_Mix/Data/Omix_rand_zscore.rds")
OV2Orig$X.2 <- NULL
OV2Orig$X.1 <- NULL

#O_V1:
#pupil corrected = pupil change from baseline
#image = triplet position (1, 2 or 3)
#newtime = time for each image in triplet (0-1250ms)
#triplet = which triplet it is (1, 2, 3 or 4)
#sub = faster way to index subjects
#triplet_trialindex = trial number based on triplet (range 1 - 96)
#timesseen = times seen the triplet (range 1- 24)
#accuracy = coding if subject scored above or below the average accuracy (0 = below, 1 = above)
#newtime2 = time for each triplet (0-3750ms)
#newtime3 = recode time: 500ms, and then 750ms (0-1250ms)
#timecode2 = recode time: 500ms, and then 750ms (0-1250ms)
#timecode3 = time for each triplet (0-3750ms)

#O_V2:
#pupil corrected = baseline is each image
#pupil corrected 2 = baseline first image of triplet
#pupil corrected 3 = baseline using predicting image of pair
#phase = 0 = familiarzation, 1 = test
#imagetype = first, second or third image in triplet
#timesseen = times seen the triplet (range 1- 20)
#trialaccuracy = if test phase trial was right or wrong

#OMix:
#pupil corrected = baseline is each image
#pupil corrected 2 = baseline first image of triplet
#block = 1 = triplet, 2 = random
#imageseq = first, second or third image in triplet
#timesseen = times seen the triplet (range 1- 20)
#TRIP_TRIAL_INDEX = correct triplet trial number
#TIMECODE2 = correct 0 - 3754ms
```

Setting color palettes
```{r}
#colors
color.t <- c("#FFCC00", "#ff9900","#FF6600") 
color.a <- c("#FFCC00", "#ff9900") 
color.aa <- c("#bacfe3", "#2875be")  #blue
color.ba <- c("#f15e6a", "#9c2b35")  #red
color.trip <- c("#c9e29f","#58a329","#327508")  #triplet green
color.ran <- c("#ddcfe8", "#7c60c3","#481f9d")  #random purple
```

Oranges V1 Graphs
```{r}
a1 <- OV1Orig

#histogram of accuracy
OV1accuracy = read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/Oranges_accuracy.csv")
OV1accuracy<-OV1accuracy[!(OV1accuracy$subject==2 |OV1accuracy$subject==11|OV1accuracy$subject==33 |OV1accuracy$subject==38),] #remove bad subjects
c <- mean(OV1accuracy$accuracy)

ggplot(OV1accuracy,aes(OV1accuracy$accuracy))+geom_histogram()+
  scale_y_continuous(limits=c(0,10),breaks=seq(0,10,1))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Histogram of accuracy")+
  labs(x = "Accuracy (%)", y = "Number of participants")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_x_continuous(label=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  geom_vline(xintercept = c, linetype = "longdash", color="red",size = 1)+
  theme(plot.title = element_text(hjust = 0.5))

#timecourse
a=c(500, 1750, 3000)
b=c(1250,2500)

a2 <- ddply(a1,.(RECORDING_SESSION_LABEL,TIMECODE3),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #collapse across subjects
a3 <- ddply(a2,.(TIMECODE3),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

ggplot(a3,aes(x=TIMECODE3,y=meanPUPILSs))+geom_line()+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,0.02))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Pupil change during triplet")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_vline(xintercept = b, size = 1.5)+
  geom_vline(xintercept = a, linetype = "longdash")+
  scale_x_continuous(limits=c(0,3750),breaks=seq(0,3750,500), expand = c(0, 0))+
  scale_fill_manual(values=color.t)+scale_colour_manual(values=color.t)

#timecourse overlay
b1 <- ddply(a1,.(RECORDING_SESSION_LABEL,image,TIMECODE2),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #collapse across subjects
b2 <- ddply(b1,.(image,TIMECODE2),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

ggplot(b2,aes(x=TIMECODE2,y=meanPUPILSs,color=factor(image),fill=factor(image)))+geom_line()+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,0.02))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_vline(xintercept = 500, linetype = "longdash")+
  scale_x_continuous(limits=c(0,1250), breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_fill_manual(values=color.t, name="Image",breaks=c("1", "2","3"),labels=c("1", "2","3"))+
  guides(color=FALSE)+
  scale_colour_manual(values=color.t)+
  theme(plot.title = element_text(hjust = 0.5))

#triplet timecourse, for accuracy
c1 <- ddply(a1,.(RECORDING_SESSION_LABEL,accuracy,TIMECODE3),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #collapse across subjects
c2 <- ddply(c1,.(accuracy,TIMECODE3),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

ggplot(c2,aes(x=TIMECODE3,y=meanPUPILSs,color=factor(accuracy),fill=factor(accuracy)))+
  geom_line()+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,0.02))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Pupil change during triplet")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_vline(xintercept = b, size = 1.5)+
  geom_vline(xintercept = a, linetype = "longdash")+
  scale_x_continuous(limits=c(0,3750),breaks=seq(0,3750,500), expand = c(0, 0))+
  scale_fill_brewer(palette="Set1",name="Accuracy",breaks=c("0", "1"),labels=c("below average", "above average"))+guides(color=FALSE)+
  scale_colour_brewer(palette="Set1")+
  theme(legend.position = "bottom")
```

Oranges V1 Analyses: Accuracy
```{r}
#ACCURACY
#The average accuracy score on the test phase was 60% which is above chance (50%) (need to check if 60% is stat sig above 50%). 
OV1accuracy<-OV1accuracy[!(OV1accuracy$subject==2 |OV1accuracy$subject==11|OV1accuracy$subject==33 |OV1accuracy$subject==38),] #remove bad subjects

res <- t.test(OV1accuracy$accuracy, mu = 0.5)
res
#t = 5.23, p-value < 0.001
```

Oranges V1 Analyses: Regression
pupil change ~ accuracy + image + times seen
```{r}
#add in continuous accuracy variable
OV1Orig$accuracy2 <- 0

sub <- unique(OV1Orig$sub)
for (i in 1:length(sub)) {
  OV1Orig$accuracy2[OV1Orig$sub==sub[i]] <- OV1accuracy$accuracy[i]
}

#anticipatory period: 500ms
famtrials3 <- subset(OV1Orig, TIMECODE2 < 502)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model500 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ image + (1|sub), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit2 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model500) 

fit3 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model500) #(1|sub = intercept)

anova(fit1,fit2,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 0.026

summary(fit3) #image + accuracy + timesseen + (1 | sub)
#within a trial, pupil size increases for image seen p = 3.91e-06***
#throughout the experiment, size increases p = 0.0263*
#no diff in accuracy :( p = 0.2835

#add interaction
fit4 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model500) #(1|sub = intercept)
summary(fit4)
#nothing

#750ms
famtrials3 <- subset(OV1Orig, TIMECODE2 > 500)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model750 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ image + (1|sub), data = model750)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit21 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model750) 

fit31 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model750) #(1|sub = intercept)

anova(fit11,fit21,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 1.9e-07***

summary(fit31) #image + accuracy + timesseen + (1 | sub)
#within a trial, no pupil size increases for image seen
#throughout the experiment, size increases timesseen p = 1.93e-07
#no diff in accuracy :(

#add interaction
fit41 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model750) #(1|sub = intercept)
summary(fit41)
#nothing

```

Oranges V1: correlation pupil response and accuracy
```{r}
#entire trial
foo <- group_by(OV1Orig, sub, accuracy2) %>%
  summarise(
    pupilavg=mean(PUPIL_CORRECTED,na.rm = TRUE)
    )
foo$trial <- 1

#anticipatory period
famtrials3 <- subset(OV1Orig, TIMECODE2 < 502) 
foo2 <- group_by(famtrials3, sub, accuracy2) %>%
  summarise(
    pupilavg=mean(PUPIL_CORRECTED,na.rm = TRUE)
    )
foo2$trial <- 2
#viewing period
famtrials3 <- subset(OV1Orig, TIMECODE2 > 500)
foo3 <- group_by(famtrials3, sub, accuracy2) %>%
  summarise(
    pupilavg=mean(PUPIL_CORRECTED,na.rm = TRUE)
    )
foo3$trial <- 3

foofinal <- rbind(foo, foo2, foo3)

split <- c(`1` = "Entire trial",`2` = "Anticipatory period",`3` = "Viewing period")

ggplot(foofinal,aes(x=accuracy2,y=pupilavg))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "Accuracy (%)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent)+
  scale_x_continuous(labels=percent)+
  facet_wrap(~trial,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=14))+
  geom_smooth(method="lm", se = FALSE)
```

Oranges V2 Graphs: Timecourse 
```{r}
f1 <- OV2Orig

#ACCURACY HISTOGRAM
z1 <- ddply(f1,.(subID),summarise,accuracy=mean(subaccuracy,na.rm = TRUE)) 
dodge <- position_dodge(width=0.9)
c <- mean(z1$accuracy)
length(which(z1$accuracy > 0.5))

ggplot(z1,aes(z1$accuracy))+geom_histogram()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Histogram of accuracy")+
  labs(x = "Accuracy (%)", y = "Number of participants")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_x_continuous(label=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  geom_vline(xintercept = c, linetype = "longdash", color="red",size = 1)+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(limits=c(0,15),breaks=seq(0,15,2))

#TIMECOURSE PLOTS
g1 <- ddply(f1,.(RECORDING_SESSION_LABEL,TIMECODE,imagetype),summarise,meanPUPIL=mean(PUPIL_CORRECTED_3,na.rm = TRUE)) #collapse across trials
g2 <- ddply(g1,.(imagetype,TIMECODE),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

#overlay
ggplot(g2,aes(x=TIMECODE,y=meanPUPILSs,color=factor(imagetype),fill=factor(imagetype)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.3)+
  scale_y_continuous(labels=percent,limits=c(-.05,.05),breaks=seq(-.05,.05,0.01))+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse for trial type")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(values=color.aa,name="Image",breaks=c("0", "1","2"),labels=c("0", "1","2"))+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_color_manual(values=color.aa)+
  theme(legend.position = "bottom")

```

Oranges V2 Graphs: Timecourse with accuracy (but accuracy isn't significant so we can skip it)
```{r}
#group accuracy as above or below chance 
f1 <- OV2Orig
f1$accuracyV2 <- 0
f1$accuracyV2[f1$subaccuracy > 0.5] <- 1

#overlay above avg + below avg
h1 <- subset(f1, accuracyV2==1)
h2 <- ddply(h1,.(RECORDING_SESSION_LABEL,TIMECODE,imagetype),summarise,meanPUPIL=mean(PUPIL_CORRECTED_3,na.rm = TRUE)) #collapse across trials
h3 <- ddply(h2,.(imagetype,TIMECODE),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

h5 <- subset(f1, accuracyV2==0)
h6 <- ddply(h5,.(RECORDING_SESSION_LABEL,TIMECODE,imagetype),summarise,meanPUPIL=mean(PUPIL_CORRECTED_3,na.rm = TRUE)) #collapse across trials
h7 <- ddply(h6,.(imagetype,TIMECODE),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

#num of subjects in above acc: 
length(unique(h1$RECORDING_SESSION_LABEL))
length(unique(h5$RECORDING_SESSION_LABEL))

h3$accuracy <- 1
h7$accuracy <- 0
hfinal <- rbind(h3,h7)
trialtype <- c(`1` = "Predicting",`2` = "Predicted")

ggplot(hfinal,aes(x=TIMECODE,y=meanPUPILSs,color=factor(accuracy),fill=factor(accuracy)))+
  geom_line()+geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4)+
  scale_y_continuous(labels=percent,limits=c(-.05,.05),breaks=seq(-.05,0.05,0.01))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse for trial type")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_vline(xintercept = 500, linetype = "longdash")+
  scale_x_continuous(limits=c(0,1300),breaks=seq(0,1300,200), expand = c(0, 0))+
  facet_wrap(~imagetype,labeller = as_labeller(trialtype))+
  theme(strip.text = element_text(size=16))+
  scale_fill_brewer(palette="Set1",name="Accuracy", breaks=c("0", "1"),labels=c("below average", "above average"))+
  guides(color=FALSE)+
  scale_colour_brewer(palette="Set1")+
  theme(legend.position = "bottom")

#overlay above avg + trial type
ggplot(h3,aes(x=TIMECODE,y=meanPUPILSs,color=factor(imagetype),fill=factor(imagetype)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.3)+
  scale_y_continuous(labels=percent,limits=c(-.05,.05),breaks=seq(-.05,0.05,0.01))+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse for trial type (above average)")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(values=color.aa,name="Image",breaks=c("0","1","2"),labels=c("0", "1","2"))+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_color_manual(values=color.aa)+
  theme(legend.position = "bottom")

#overlay below avg + trial type
ggplot(h7,aes(x=TIMECODE,y=meanPUPILSs,color=factor(imagetype),fill=factor(imagetype)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.3)+
  scale_y_continuous(labels=percent,limits=c(-.05,.05),breaks=seq(-.05,0.05,0.01))+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse for trial type (below average)")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(values=color.ba,name="Image",breaks=c("0", "1","2"),labels=c("0", "1","2"))+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_color_manual(values=color.ba)+
  theme(legend.position = "bottom")

```

Oranges V2 Analyses: Accuracy
```{r}
#ACCURACY
#The average accuracy score on the test phase was 53% which is only sligh chance (50%)
z2 <- ddply(OV2Orig,.(subID),summarise,accuracy=mean(subaccuracy,na.rm = TRUE)) 

res <- t.test(z2$accuracy, mu = 0.5)
res
#t = 2.0497, p-value = 0.045

#comparing accuracy for V1 and V2 (59% vs 53%)
#accuracy on V2 is significantly worse p=0.01
t.test(OV1accuracy$accuracy, z2$accuracy, var.equal = FALSE)
```

Oranges V2 Analyses: Regression
pupil change ~ accuracy + image + times seen
```{r}
#anticipatory period: 500ms
famtrials3 <- subset(f1, TIMECODE < 502)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model500 <- ddply(famtrials3,.(subID,timesseen,imagetype,subaccuracy),summarise,meanpupil=mean(PUPIL_CORRECTED_3,na.rm = TRUE)) 

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ imagetype + (1|subID), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |subID), data = model500) #can also include accuracy as continuous
fit2 <- lmer(meanpupil ~ imagetype + subaccuracy + (1|subID), data = model500) 

fit3 <- lmer(meanpupil ~ imagetype + subaccuracy + timesseen + (1|subID), data = model500) #(1|sub = intercept)

anova(fit1,fit2,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#nothing is significant
summary(fit3)
#result: #within a trial, pupil size increases for image type p = 0.01**
#no familiarity effect size increases p = 0.79256
#no diff in accuracy :( p = 0.35073

#add interaction
fit4 <- lmer(meanpupil ~ imagetype * subaccuracy * timesseen + (1|subID), data = model500) #(1|sub = intercept)
summary(fit4)
#nothing

#750ms
famtrials3 <- subset(f1, TIMECODE > 500)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model750 <- ddply(famtrials3,.(subID,timesseen,imagetype,subaccuracy),summarise,meanpupil=mean(PUPIL_CORRECTED_3,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ imagetype + (1|subID), data = model750)

#fit2 <- lmer(meanpupil ~ imagetype + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit21 <- lmer(meanpupil ~ imagetype + subaccuracy + (1|subID), data = model750) 

fit31 <- lmer(meanpupil ~ imagetype + subaccuracy + timesseen + (1|subID), data = model750) #(1|sub = intercept)

anova(fit11,fit21,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 0.01***

summary(fit31) #image + accuracy + timesseen + (1 | sub)
#within a trial, pupil size increased for image type p = 0.0097 **
#familiarty effect p = 0.013 *
#no diff in accuracy :(

#add interaction
fit41 <- lmer(meanpupil ~ imagetype * subaccuracy * timesseen + (1|subID), data = model750) #(1|sub = intercept)
summary(fit41)
#nothing

```

Oranges Mix Graphs
```{r}
#only keep center looks
orig2 <- OmixOrig
a <- which(orig2$RIGHT_GAZE_X < 440)
orig2 <- orig2[-c(a), ]
a <- which(orig2$RIGHT_GAZE_Y < 312)
orig2 <- orig2[-c(a), ]
a <- which(orig2$RIGHT_GAZE_X > 840)
orig2 <- orig2[-c(a), ]
a <- which(orig2$RIGHT_GAZE_Y > 712)
orig2 <- orig2[-c(a), ]

block1 <- subset(orig2, TRIAL_INDEX < 241)
block2 <- subset(orig2, TRIAL_INDEX > 240)

###Timecourse
#block 1 overlay
d1 <- ddply(block1,.(subID,TIMECODE,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
d2 <- ddply(d1,.(TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(d2,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,.02))+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse Block 1 (Triplet)")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.trip)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_color_manual(values=color.trip)+
  theme(legend.position = "bottom")

#block 2 overlay
goo <- ddply(block2,.(subID,TIMECODE,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
goo2 <- ddply(goo,.(TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(goo2,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,.02))+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse Block 2 (Random)")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.ran)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  theme(legend.position = "bottom")+
  scale_colour_manual(values=color.ran)

#timecourse block 1 + block 2 overlay

coo1 <- ddply(block1,.(subID,TIMECODE2),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
coo2 <- ddply(block2,.(subID,TIMECODE2),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
coo1$block <- 1
coo2$block <- 2
coo3 <- ddply(coo1,.(TIMECODE2,block),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))
coo4 <- ddply(coo2,.(TIMECODE2,block),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

a = c(500,1750,3000)
aa = c(1250,2500)

coo5 <- rbind(coo3,coo4)

ggplot(coo5,aes(x=TIMECODE2,y=meanPUPIL,color=factor(block),fill=factor(block)))+geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+ggtitle("Timecourse")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.4)+
  scale_x_continuous(limits=c(0,3754),breaks=seq(0,3754,500), expand = c(0, 0))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,.02))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Accent",name="Block",breaks=c("1","2"),labels=c("Triplet", "Random"))+
  scale_color_brewer(palette="Accent")+
  theme(legend.position = "bottom")+
  geom_vline(xintercept = a, linetype = "longdash")+
  geom_vline(xintercept = aa, size =1)
```

Oranges Mix Analyses: Regression
pupil change ~ image + times seen 
anticipatory period: 500ms
```{r}
#triplet block
famtrials3 <- subset(Omix.Trip, TIMECODE < 502)

#participant (1-53), timesseen (1-24), image position (1-3), block (0,1), accuracy
model500 <- ddply(famtrials3,.(subID,timesseen,imageseq,block),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 
model500$block <- model500$block-1

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ imageseq + (1|subID), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |subID), data = model500) #can also include accuracy as continuous

fit3 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model500) #(1|sub = intercept)

anova(fit1,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit3 is better
summary(fit3)
#Result: image seq is significant (B= 0.005316, p = 0.0002) and familiarity effect (B=0.0006058, p=0.0028)

#add interaction
fit4 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model500) #(1|sub = intercept)
summary(fit4)
#sig interaction for imageseq:timessseen p = 0.0375

#random block
famtrials3 <- subset(Omix.Rand, TIMECODE < 502)

#fill in timesseen
famtrials3$timesseen[famtrials3$TRIAL_INDEX < 253] <- 1
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 252 & famtrials3$TRIAL_INDEX < 265] <- 2
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 264 & famtrials3$TRIAL_INDEX < 277] <- 3
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 276 & famtrials3$TRIAL_INDEX < 289] <- 4
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 288 & famtrials3$TRIAL_INDEX < 301] <- 5
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 300 & famtrials3$TRIAL_INDEX < 313] <- 6
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 312 & famtrials3$TRIAL_INDEX < 325] <- 7
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 324 & famtrials3$TRIAL_INDEX < 337] <- 8
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 336 & famtrials3$TRIAL_INDEX < 349] <- 9
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 348 & famtrials3$TRIAL_INDEX < 361] <- 10
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 360 & famtrials3$TRIAL_INDEX < 373] <- 11
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 372 & famtrials3$TRIAL_INDEX < 385] <- 12
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 384 & famtrials3$TRIAL_INDEX < 397] <- 13
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 396 & famtrials3$TRIAL_INDEX < 409] <- 14
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 408 & famtrials3$TRIAL_INDEX < 421] <- 15
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 420 & famtrials3$TRIAL_INDEX < 433] <- 16
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 432 & famtrials3$TRIAL_INDEX < 445] <- 17
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 444 & famtrials3$TRIAL_INDEX < 457] <- 18
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 456 & famtrials3$TRIAL_INDEX < 469] <- 19
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 468] <- 20

#participant (1-53), timesseen (1-24), image position (1-3), block (0,1), accuracy
model500 <- ddply(famtrials3,.(subID,timesseen,imageseq,block),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ imageseq + (1|subID), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |subID), data = model500) #can also include accuracy as continuous

fit3 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model500) #(1|sub = intercept)

anova(fit1,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit1 and fit3 are the same
summary(fit3)
#image seq is significant (B= 0.009396, p = 0.0176) even for random it gets larger which goes against our hypothesis

#add interaction
fit4 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model500) #(1|sub = intercept)
summary(fit4)
#nothing
```

Oranges Mix Analyses: Regression
pupil change ~ image + times seen 
viewing period: 750ms
```{r}
#triplet block
famtrials3 <- subset(Omix.Trip, TIMECODE > 500)

#participant (1-53), triplet presentation (1-24), image position (1-3)
model750 <- ddply(famtrials3,.(subID,timesseen,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ imageseq + (1|subID), data = model750)

fit31 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model750) #(1|sub = intercept)

anova(fit11,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit31 is better

summary(fit31) 
#Result: familiarity effect size increases timesseen (B=0.0007522, p = 0.00126)

#add interaction
fit41 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model750) #(1|sub = intercept)
summary(fit41)
#sig interaction for imageseq:timessseen p = 0.04

#random block
famtrials3 <- subset(Omix.Rand, TIMECODE > 500)

#fill in timesseen
famtrials3$timesseen[famtrials3$TRIAL_INDEX < 253] <- 1
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 252 & famtrials3$TRIAL_INDEX < 265] <- 2
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 264 & famtrials3$TRIAL_INDEX < 277] <- 3
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 276 & famtrials3$TRIAL_INDEX < 289] <- 4
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 288 & famtrials3$TRIAL_INDEX < 301] <- 5
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 300 & famtrials3$TRIAL_INDEX < 313] <- 6
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 312 & famtrials3$TRIAL_INDEX < 325] <- 7
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 324 & famtrials3$TRIAL_INDEX < 337] <- 8
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 336 & famtrials3$TRIAL_INDEX < 349] <- 9
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 348 & famtrials3$TRIAL_INDEX < 361] <- 10
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 360 & famtrials3$TRIAL_INDEX < 373] <- 11
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 372 & famtrials3$TRIAL_INDEX < 385] <- 12
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 384 & famtrials3$TRIAL_INDEX < 397] <- 13
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 396 & famtrials3$TRIAL_INDEX < 409] <- 14
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 408 & famtrials3$TRIAL_INDEX < 421] <- 15
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 420 & famtrials3$TRIAL_INDEX < 433] <- 16
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 432 & famtrials3$TRIAL_INDEX < 445] <- 17
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 444 & famtrials3$TRIAL_INDEX < 457] <- 18
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 456 & famtrials3$TRIAL_INDEX < 469] <- 19
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 468] <- 20

#participant (1-53), triplet presentation (1-24), image position (1-3)
model750 <- ddply(famtrials3,.(subID,timesseen,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ imageseq + (1|subID), data = model750)

fit31 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model750) #(1|sub = intercept)

anova(fit11,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit11 and fit31 are the same

summary(fit31) 
#Result: nothing

#add interaction
fit41 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model750) #(1|sub = intercept)
summary(fit41)
#nothing

```

#### Siegelman et al 2018 compute their “online measure of learning.” ####
It would be a nice way of creating an intersection with another paper in the literature. I think it’s something that we could put in supplementary or just have a short paragraph saying that we are following their method and we find X,Y,Z with a key graph. What do you think about this? 
Also, we look at trajectory differences by looking at the effect of familiarity on the pupil response but we could make a more explicit connection to Siegelman et al 2018 by emphasizing it more and noting that this measure looks at the trajectory of learning, Moreover, if you computed the online measure, we could look at how that changes with repetition or familiarity. 

In the Siegelman paper, because they measured RT (i.e. smaller RT means faster and better performance) then a positive online measure score means better learning because RT for the 1st position is larger compared to the 2nd and 3rd. 

Oranges V1
```{r}
#ANTICIPATORY PERIOD
ant <- subset(OV1Orig, TIMECODE2 < 502)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(ant, sub, TRIALNUM, triplet_trialindex, image, timesseen) %>%
  summarise(
    pupilavg = mean(newpupil, na.rm = TRUE)
  )

# using average of 2 and 3
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = mean(pupilavg[which(image!=1)])
  )

# just 2
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = pupilavg[which(image==2)]
  )

# just 3
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = pupilavg[which(image==3)]
  )

poo2$onlineSL <- poo2$image1 - poo2$image23

poo3 <- group_by(poo2, sub, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, sub, image, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, image, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(image),fill=factor(image)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  scale_x_continuous(limits=c(1,24),breaks=seq(1,24,1))+
  geom_smooth(method="lm", se = FALSE)+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,24),breaks=seq(1,24,1))+
  scale_y_continuous(limits=c(-.1,.03),breaks=seq(-.1,.03,.01))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)

# For each individual, we averaged the difference pupil change between predictable and unpredictable shapes for entire block and see if it correlates their 2-AFC offline test score 
loo <- group_by(poo3, sub) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE)
  )
names(loo)[1] <- "subject"

loo2 <- merge(loo, OV1accuracy, by = "subject")

# run correlation
cor.test(loo2$meanOnlineSL, loo2$accuracy) #not significant

ggplot(loo2,aes(x=accuracy,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  ggtitle("Anticipatory period")+
  labs(x = "Accuracy on test phase", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_x_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_y_continuous(limits=c(-.1,.07),breaks=seq(-.1,.07,.02))+
  geom_smooth(method="lm", se = FALSE)

######## VIEWING PERIOD  
view <- subset(OV1Orig, TIMECODE2 > 500)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(view, sub, TRIALNUM, triplet_trialindex, image, timesseen) %>%
  summarise(
    pupilavg = mean(newpupil, na.rm = TRUE)
  )

# use mean of 2 and 3
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = mean(pupilavg[which(image!=1)])
  )

# just 2
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = pupilavg[which(image==2)]
  )

# just 3
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = pupilavg[which(image==3)]
  )

poo2$onlineSL <- poo2$image1 - poo2$image23

poo3 <- group_by(poo2, sub, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, sub, image, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, image, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(image),fill=factor(image)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  scale_x_continuous(limits=c(1,24),breaks=seq(1,24,1))+
  geom_smooth(method="lm", se = FALSE)+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,24),breaks=seq(1,24,1))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)

# For each individual, we averaged the difference pupil change between predictable and unpredictable shapes for entire block and see if it correlates their 2-AFC offline test score 
loo <- group_by(poo3, sub) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE)
  )
names(loo)[1] <- "subject"

loo2 <- merge(loo, OV1accuracy, by = "subject")

# run correlation
cor.test(loo2$meanOnlineSL, loo2$accuracy) #not significant

ggplot(loo2,aes(x=accuracy,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  ggtitle("Viewing period")+
  labs(x = "Accuracy on test phase", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_x_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_y_continuous(limits=c(-.05,.03),breaks=seq(-.05,.03,.01))+
  geom_smooth(method="lm", se = FALSE)
```

Oranges V2
```{r}
#ANTICIPATORY PERIOD
ant2 <- subset(OV2Orig, TIMECODE < 502)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(ant2, subID, TRIAL_INDEX, imagetype, timesseen) %>%
  summarise(
    pupilavg = mean(PUPIL_CORRECTED_3, na.rm = TRUE)
  )
# add in pair trial index
poo$pair_trialindex <- 0

subs <- unique(poo$subID)
for (j in 1:length(subs)) {
for (i in 1:144) {
  if (length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*2)-1)) > 0 & length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*2))) > 0) {
    poo$pair_trialindex[(poo$TRIAL_INDEX ==(i*2)-1 | poo$TRIAL_INDEX ==(i*2)) & poo$subID==subs[j]] <- i
}}}

# remove rows that only have info from 1 image in a pair
poo <- subset(poo, pair_trialindex !=0)

poo2 <- group_by(poo, subID, pair_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imagetype==1)],
    image2 = pupilavg[which(imagetype==2)]
  )

poo2$onlineSL <- poo2$image1 - poo2$image2
poo2 <- na.omit(poo2)

poo3 <- group_by(poo2, subID, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, subID, imagetype, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, imagetype, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(imagetype),fill=factor(imagetype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  geom_smooth(method="lm", se = FALSE)+
  scale_x_continuous(limits=c(1,36),breaks=seq(1,36,2))+
  scale_y_continuous(limits=c(-0.05,.05),breaks=seq(-0.05,.05,.01))+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,36),breaks=seq(1,36,2))+
  scale_y_continuous(limits=c(-.07,.05),breaks=seq(-.07,.05,.01))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)

# For each individual, we averaged the difference pupil change between predictable and unpredictable shapes for entire block and see if it correlates their 2-AFC offline test score 
loo <- group_by(poo3, subID) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE)
  )

loo2 <- merge(loo, z2, by = "subID")

# run correlation
cor.test(loo2$meanOnlineSL, loo2$accuracy) #not significant

ggplot(loo2,aes(x=accuracy,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  ggtitle("Anticipatory period")+
  labs(x = "Accuracy on test phase", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_x_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_y_continuous(limits=c(-.1,.07),breaks=seq(-.1,.07,.02))+
  geom_smooth(method="lm", se = FALSE)

#VIEWING PERIOD  
view2 <- subset(OV2Orig, TIMECODE > 500)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(view2, subID, TRIAL_INDEX, imagetype, timesseen) %>%
  summarise(
    pupilavg = mean(PUPIL_CORRECTED_3, na.rm = TRUE)
  )
# add in pair trial index
poo$pair_trialindex <- 0

subs <- unique(poo$subID)
for (j in 1:length(subs)) {
for (i in 1:144) {
  if (length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*2)-1)) > 0 & length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*2))) > 0) {
    poo$pair_trialindex[(poo$TRIAL_INDEX ==(i*2)-1 | poo$TRIAL_INDEX ==(i*2)) & poo$subID==subs[j]] <- i
}}}

# remove rows that only have info from 1 image in a pair
poo <- subset(poo, pair_trialindex !=0)

poo2 <- group_by(poo, subID, pair_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imagetype==1)],
    image2 = pupilavg[which(imagetype==2)]
  )

poo2$onlineSL <- poo2$image1 - poo2$image2
poo2 <- na.omit(poo2)

poo3 <- group_by(poo2, subID, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, subID, imagetype, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, imagetype, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(imagetype),fill=factor(imagetype)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  geom_smooth(method="lm", se = FALSE)+
  scale_x_continuous(limits=c(1,36),breaks=seq(1,36,2))+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,36),breaks=seq(1,36,2))+
  scale_y_continuous(limits=c(-.1,.06),breaks=seq(-.1,.06,.02))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)

# For each individual, we averaged the difference pupil change between predictable and unpredictable shapes for entire block and see if it correlates their 2-AFC offline test score 
loo <- group_by(poo3, subID) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE)
  )

loo2 <- merge(loo, z2, by = "subID")

# run correlation
cor.test(loo2$meanOnlineSL, loo2$accuracy) #not significant

ggplot(loo2,aes(x=accuracy,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  ggtitle("Viewing period")+
  labs(x = "Accuracy on test phase", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_x_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_y_continuous(limits=c(-.1,.07),breaks=seq(-.1,.07,.02))+
  geom_smooth(method="lm", se = FALSE)
```

Oranges Mix: Triplet block
```{r}
#ANTICIPATORY PERIOD
ant3 <- subset(Omix.Trip, TIMECODE < 502)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(ant3, subID, TRIAL_INDEX, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(PUPIL_CORRECTED_2, na.rm = TRUE)
  )

# add in triplet trial index
poo$triplet_trialindex <- 0

subs <- unique(poo$subID)
for (j in 1:length(subs)) {
for (i in 1:80) {
  if (length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*3)-1)) > 0 & length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*3)-2)) > 0 & length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*3))) > 0) {
    poo$triplet_trialindex[(poo$TRIAL_INDEX ==(i*3)-2 | poo$TRIAL_INDEX ==(i*3)-1 | poo$TRIAL_INDEX ==(i*3)) & poo$subID==subs[j]] <- i
    
}}}

poo <- subset(poo, triplet_trialindex !=0)

# use mean of both image 2 and 3
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = mean(pupilavg[which(imageseq!=1)])
  )

# just 2
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = pupilavg[which(imageseq==2)]
  )

# just 3
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = pupilavg[which(imageseq==3)]
  )

poo2$onlineSL <- poo2$image1 - poo2$image23

poo3 <- group_by(poo2, subID, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, subID, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, imageseq, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  geom_smooth(method="lm", se = FALSE)+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  scale_y_continuous(limits=c(-.04,.03),breaks=seq(-.04,.03,.01))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)

#VIEWING PERIOD  
view3 <- subset(Omix.Trip, TIMECODE2 > 500)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(view3, subID, TRIAL_INDEX, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(PUPIL_CORRECTED_2, na.rm = TRUE)
  )

# add in triplet trial index
poo$triplet_trialindex <- 0

subs <- unique(poo$subID)
for (j in 1:length(subs)) {
for (i in 1:80) {
  if (length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*3)-1)) > 0 & length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*3)-2)) > 0 & length(which(poo$TRIAL_INDEX[poo$subID==subs[j]]==(i*3))) > 0) {
    poo$triplet_trialindex[(poo$TRIAL_INDEX ==(i*3)-2 | poo$TRIAL_INDEX ==(i*3)-1 | poo$TRIAL_INDEX ==(i*3)) & poo$subID==subs[j]] <- i
    
}}}

poo <- subset(poo, triplet_trialindex !=0)

# use both image 2 and 3
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = mean(pupilavg[which(imageseq!=1)])
  )

# just 2
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = pupilavg[which(imageseq==2)]
  )

# just 3
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = pupilavg[which(imageseq==3)]
  )

poo2$onlineSL <- poo2$image1 - poo2$image23

poo3 <- group_by(poo2, subID, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, subID, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, imageseq, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  geom_smooth(method="lm", se = FALSE)+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  scale_y_continuous(limits=c(-.03,.05),breaks=seq(-.03,.05,.01))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)

#Remove trial 1
poo5 <- subset(poo4, timesseen > 1)
ggplot(poo5,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  scale_y_continuous(limits=c(-.03,.05),breaks=seq(-.03,.05,.01))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo5$timesseen, poo5$meanOnlineSL)
```

Oranges Mix: Random block
```{r}
#fill in timesseen
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX < 253] <- 1
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 252 & Omix.Rand$TRIAL_INDEX < 265] <- 2
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 264 & Omix.Rand$TRIAL_INDEX < 277] <- 3
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 276 & Omix.Rand$TRIAL_INDEX < 289] <- 4
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 288 & Omix.Rand$TRIAL_INDEX < 301] <- 5
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 300 & Omix.Rand$TRIAL_INDEX < 313] <- 6
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 312 & Omix.Rand$TRIAL_INDEX < 325] <- 7
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 324 & Omix.Rand$TRIAL_INDEX < 337] <- 8
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 336 & Omix.Rand$TRIAL_INDEX < 349] <- 9
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 348 & Omix.Rand$TRIAL_INDEX < 361] <- 10
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 360 & Omix.Rand$TRIAL_INDEX < 373] <- 11
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 372 & Omix.Rand$TRIAL_INDEX < 385] <- 12
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 384 & Omix.Rand$TRIAL_INDEX < 397] <- 13
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 396 & Omix.Rand$TRIAL_INDEX < 409] <- 14
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 408 & Omix.Rand$TRIAL_INDEX < 421] <- 15
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 420 & Omix.Rand$TRIAL_INDEX < 433] <- 16
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 432 & Omix.Rand$TRIAL_INDEX < 445] <- 17
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 444 & Omix.Rand$TRIAL_INDEX < 457] <- 18
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 456 & Omix.Rand$TRIAL_INDEX < 469] <- 19
Omix.Rand$timesseen[Omix.Rand$TRIAL_INDEX > 468] <- 20

#ANTICIPATORY PERIOD
ant4 <- subset(Omix.Rand, TIMECODE < 502)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(ant4, subID, TRIAL_INDEX, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(PUPIL_CORRECTED_2, na.rm = TRUE)
  )

poo$TRIAL_INDEX_2 <- poo$TRIAL_INDEX - 240

# add in triplet trial index
poo$triplet_trialindex <- 0

subs <- unique(poo$subID)
for (j in 1:length(subs)) {
for (i in 1:80) {
  if (length(which(poo$TRIAL_INDEX_2[poo$subID==subs[j]]==(i*3)-1)) > 0 & length(which(poo$TRIAL_INDEX_2[poo$subID==subs[j]]==(i*3)-2)) > 0 & length(which(poo$TRIAL_INDEX_2[poo$subID==subs[j]]==(i*3))) > 0) {
    poo$triplet_trialindex[(poo$TRIAL_INDEX_2 ==(i*3)-2 | poo$TRIAL_INDEX_2 ==(i*3)-1 | poo$TRIAL_INDEX_2 ==(i*3)) & poo$subID==subs[j]] <- i
    
}}}

poo <- subset(poo, triplet_trialindex !=0)

# use both image 2 and 3
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = mean(pupilavg[which(imageseq!=1)])
  )

# just 2
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = pupilavg[which(imageseq==2)]
  )

# just 3
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = pupilavg[which(imageseq==3)]
  )

poo2$onlineSL <- poo2$image1 - poo2$image23

poo3 <- group_by(poo2, subID, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, subID, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, imageseq, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  geom_smooth(method="lm", se = FALSE)+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Anticipatory period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  scale_y_continuous(limits=c(-.08,.03),breaks=seq(-.08,.03,.01))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)

#VIEWING PERIOD  
view4 <- subset(Omix.Rand, TIMECODE2 > 500)

#online measure of SL = pupil change for 1st position - mean(pupil change for 2nd and 3rd position)
poo <- group_by(view4, subID, TRIAL_INDEX, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(PUPIL_CORRECTED_2, na.rm = TRUE)
  )

poo$TRIAL_INDEX_2 <- poo$TRIAL_INDEX - 240

# add in triplet trial index
poo$triplet_trialindex <- 0

subs <- unique(poo$subID)
for (j in 1:length(subs)) {
for (i in 1:80) {
  if (length(which(poo$TRIAL_INDEX_2[poo$subID==subs[j]]==(i*3)-1)) > 0 & length(which(poo$TRIAL_INDEX_2[poo$subID==subs[j]]==(i*3)-2)) > 0 & length(which(poo$TRIAL_INDEX_2[poo$subID==subs[j]]==(i*3))) > 0) {
    poo$triplet_trialindex[(poo$TRIAL_INDEX_2 ==(i*3)-2 | poo$TRIAL_INDEX_2 ==(i*3)-1 | poo$TRIAL_INDEX_2 ==(i*3)) & poo$subID==subs[j]] <- i
    
}}}

poo <- subset(poo, triplet_trialindex !=0)

# use both image 2 and 3
poo2 <- group_by(poo, subID, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(imageseq==1)],
    image23 = mean(pupilavg[which(imageseq!=1)])
  )

# just 2
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = pupilavg[which(image==2)]
  )

# just 3
poo2 <- group_by(poo, sub, triplet_trialindex, timesseen) %>%
  summarise(
    image1 = pupilavg[which(image==1)],
    image23 = pupilavg[which(image==3)]
  )poo2$onlineSL <- poo2$image1 - poo2$image23

poo3 <- group_by(poo2, subID, timesseen) %>%
  summarise(
    onlineSL = mean(onlineSL, na.rm = TRUE)
  )

poo4 <- group_by(poo3, timesseen) %>%
  summarise(
    meanOnlineSL = mean(onlineSL, na.rm = TRUE),
    seOnlineSL=sd(onlineSL, na.rm = TRUE)/sqrt(length(onlineSL))
  )

foo <- group_by(poo, subID, imageseq, timesseen) %>%
  summarise(
    pupilavg = mean(pupilavg, na.rm = TRUE)
  )

foo2 <- group_by(foo, imageseq, timesseen) %>%
  summarise(
    meanPUPIL = mean(pupilavg, na.rm = TRUE),
    sePUPIL=sd(pupilavg, na.rm = TRUE)/sqrt(length(pupilavg))
  )

#Fig 2 from the paper = plot pupil change for each block, line graph, colored by position
ggplot(foo2,aes(x=timesseen,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="bottom")+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  geom_smooth(method="lm", se = FALSE)+
  scale_fill_manual(values=color.t )+
  guides(fill=FALSE)+
  scale_colour_manual(values=color.t, name="Image Position",breaks=c("1", "2","3"),labels=c("1", "2","3"))

#Fig 3 from the paper = plot online measure of SL for each block
ggplot(poo4,aes(x=timesseen,y=meanOnlineSL))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point(size = 5)+
  geom_line(size = 1.5)+
  ggtitle("Viewing period")+
  labs(x = "Number of times seen", y = "Online measure of SL")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0.5))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  geom_ribbon(aes(ymin=meanOnlineSL-seOnlineSL,ymax=meanOnlineSL+seOnlineSL),alpha=0.4)+
  scale_x_continuous(limits=c(1,20),breaks=seq(1,20,1))+
  scale_y_continuous(limits=c(-.05,.05),breaks=seq(-.05,.05,.01))+
  geom_smooth(method="lm", se = FALSE)

cor.test(poo4$timesseen, poo4$meanOnlineSL)
```

