---
title: "Cog Lunch Graphs V2"
author: "Felicia Zhang"
date: '2017-02-27'
output: html_document
---

Now we are removing accuracy since it doesn't come out in the model
```{r setup, include=FALSE}

library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)

#famphase1 = raw fam phase, only been preprocessed nothing else done
#famphase2 = including newtime and newtime2
#famphase3 = same as famphase2 + new timecode

#famphase4 = raw fam phase, actually recoded trials based on original data so that new timecourse is much smoother
#famphase5 = includes newpupil where pupil size for triplet is calculated for baseline of first image

#1. load data (master)
famtrials <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/Oranges_famphase5.csv")   
famtrials$X.1 <- NULL
famtrials$HTARGET_DISTANCE <- NULL
famtrials$HTARGET_X <- NULL
famtrials$HTARGET_Y <- NULL
famtrials$LEFT_GAZE_X <- NULL
famtrials$LEFT_GAZE_Y <- NULL
famtrials$LEFT_PUPIL_SIZE <- NULL
famtrials$TRIAL_LABEL <- NULL
famtrials$LEFT_IN_BLINK <- NULL
names(famtrials)[11]<-"sub"

poo <- famtrials
#pupil corrected = pupil change from baseline
#image = triplet position (1, 2 or 3)
#newtime = time for each image in triplet (0-1250ms)
#triplet = which triplet it is (1, 2, 3 or 4)
#sub = faster way to index subjects
#triplet_trialindex = trial number based on triplet (range 1 - 96)
#timesseen = times seen the triplet (range 1- 24)
#accuracy = coding if subject scored above or below the average accuracy (0 = below, 1 = above)
#newtime2 = time for each triplet (0-3750ms)
#newtime3 = recode time: 500ms, and then 750ms (0-1250ms)
#timecode2 = recode time: 500ms, and then 750ms (0-1250ms)
#timecode3 = time for each triplet (0-3750ms)

a <- c(1250,2500,3750) #image onset
b <- c(500,1750,3000)

#colors
color.v1 <- c("#ffcc66", "#ff9900","#cc3300") #triplet position
#color.v2 <- c("#ccffff", "#99ccff","#336699") #good
color.v3 <- c("#ff9900", "#99ccff") #group
```

Modelling: pupil size based on image position, random effect for subjects
can also add in: trial number, triplet times seen, 
```{r}
#add in continuous accuracy variable
famtrials2 <- famtrials
acc <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/Oranges_accuracy.csv")
acc<-acc[!(acc$subject==2 |acc$subject==11|acc$subject==33 |acc$subject==38),]
famtrials2$accuracy2 <- 0
sub <- unique(famtrials2$sub)

for (i in 1:length(sub)) {
  famtrials2$accuracy2[famtrials2$sub==sub[i]] <- acc$accuracy[i]
}

#500ms
famtrials3 <- subset(famtrials2, TIMECODE2 < 502)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model500 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ image + (1|sub), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit2 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model500) 

fit3 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model500) #(1|sub = intercept)


anova(fit1,fit2,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 0.026

summary(fit3) #image + accuracy + timesseen + (1 | sub)
#within a trial, pupil size increases for image seen p = 3.91e-06***
#throughout the experiment, size increases p = 0.0263*
#no diff in accuracy :( p = 0.2835

#add interaction
fit4 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model500) #(1|sub = intercept)
summary(fit4)
#nothing

#750ms
famtrials3 <- subset(famtrials2, TIMECODE2 > 500)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model750 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ image + (1|sub), data = model750)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit21 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model750) 

fit31 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model750) #(1|sub = intercept)

anova(fit11,fit21,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 1.9e-07***

summary(fit31) #image + accuracy + timesseen + (1 | sub)
#within a trial, no pupil size increases for image seen
#throughout the experiment, size increases timesseen p = 1.93e-07
#no diff in accuracy :(

#add interaction
fit41 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model750) #(1|sub = intercept)
summary(fit41)
#nothing

```


run the model again with just second and third images? 
raw pupil size
```{r}
#add in continuous accuracy variable
famtrials2 <- famtrials
acc <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/Oranges_accuracy.csv")
acc<-acc[!(acc$subject==2 |acc$subject==11|acc$subject==33 |acc$subject==38),]
famtrials2$accuracy2 <- 0
sub <- unique(famtrials2$sub)

for (i in 1:length(sub)) {
  famtrials2$accuracy2[famtrials2$sub==sub[i]] <- acc$accuracy[i]
}

#500ms
famtrials3 <- subset(famtrials2, TIMECODE2 < 502)
#only looking at second and third images

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model500 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 
model500 <- subset(model500, image > 1)

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ image + (1|sub), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit2 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model500) 

fit3 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model500) #(1|sub = intercept)


anova(fit1,fit2,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 0.026*

summary(fit3) #image + accuracy + timesseen + (1 | sub)
#within a trial, pupil size increases for image seen p = 0.0194*
#throughout the experiment, size increases times seen p = 0.0261*
#no diff in accuracy :( p = 0.2851

#add interaction
fit4 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model500) #(1|sub = intercept)
summary(fit4)
#no interaction

#750ms
famtrials3 <- subset(famtrials2, TIMECODE2 > 500)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model750 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 
model750 <- subset(model750, image > 1)

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ image + (1|sub), data = model750)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit21 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model750) 

fit31 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model750) #(1|sub = intercept)

anova(fit11,fit21,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 5.185e-06***

summary(fit31) #image + accuracy + timesseen + (1 | sub)
#within a trial, no pupil size increases for image seen p = 0.183
#throughout the experiment, size increases timesseen p = 5.2e-06
#no diff in accuracy :( p = 0.693

#add interaction
fit41 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model750) #(1|sub = intercept)
summary(fit41)
#nothing


#SUMMARY: when removing image 1, all the effects stay the same except for the interaction
```


Triplet timecourse graph of triplet so that all the pupil_corrected are relative to the first baseline
removing first triplet since we're missing it
```{r}
# poo$newpupil <- 0
# 
# poo <- subset(poo, triplet_trialindex > 1) #removing first triplet Ss see since it's missing the first image
# trials <- unique(poo$triplet_trialindex)
# subs <- unique(poo$sub)
# 
# for (j in 1:length(subs)) {
#   print(j)
# for (i in 1:length(trials)) { #for each trial
#   q <- min(which(poo$triplet_trialindex == trials[i] & poo$sub == subs[j]))
#   baseline <- poo$rollmean100ms[(q):(q+250)] #gets 500 ms of start of trial as baseline
#   baselineavg <- mean(baseline)
#   poo$newpupil[poo$triplet_trialindex == trials[i] & poo$sub == subs[j]] <- (poo$rollmean100ms[poo$triplet_trialindex == trials[i] & poo$sub == subs[j]] - baselineavg) / baselineavg
#   print(i)
# }}

fam3 <- ddply(poo,.(RECORDING_SESSION_LABEL,TIMECODE3),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #collapse across subjects
goo <- ddply(fam3,.(TIMECODE3),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

  ggplot(goo,aes(x=TIMECODE3,y=meanPUPILSs))+geom_line(colour="#ff9900")+
    geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4, fill="#ff9900")+
     scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,0.05))+theme_bw()+theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Pupil change during triplet")+
    labs(x = "Time (ms)", y = "Change from baseline")+
    theme(plot.title = element_text(face="bold", size=20, hjust=0))+
    theme(axis.title = element_text(face="bold", size=20))+ 
    theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
    theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+geom_vline(xintercept = a, size = 1.5)+geom_vline(xintercept = b, linetype = "longdash")+scale_x_continuous(limits=c(0,3750),breaks=seq(0,3750,500), expand = c(0, 0))

```

overlay graph V2
```{r}
#overlay triplet image 1,2 3
fam3 <- ddply(poo,.(sub,TIMECODE3),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #
gooD <- ddply(fam3,.(TIMECODE3),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL)))

img1 <- subset(gooD, TIMECODE3 < 1251)
img1$image <- 1
img2 <- subset(gooD, TIMECODE3 < 2503 & TIMECODE3 > 1250 )
img2$TIMECODE3 <- seq(0, 1250, by = 2)
img2$image <- 2
img3 <- subset(gooD, TIMECODE3 > 2502 )
img3$TIMECODE3 <- seq(0, 1250, by = 2)
img3$image <- 3

goo2 <- rbind(img1,img2,img3)  
#plot

  ggplot(goo2,aes(x=TIMECODE3,y=meanPUPILSs,color=factor(image),fill=factor(image)))+
    geom_line()+
    scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
    scale_colour_manual(values=color.v1)+
    geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.3)+
    scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,.05))+
    guides(color=FALSE)+
    theme_bw()+theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Pupil change during triplet")+
    labs(x = "Time (ms)", y = "Change from baseline")+
    theme(plot.title = element_text(face="bold", size=20, hjust=0))+
    theme(axis.title = element_text(face="bold", size=20))+ 
    theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
    theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
    scale_fill_manual(values=color.v1,name="Image in triplet",breaks=c("1", "2","3"),labels=c("1", "2","3"))+geom_vline(xintercept = 500)

```

times seen triplet for 500ms for new timecode, baselining everything to the first image in triplet
```{r}
famtrials2 <- subset(poo, TIMECODE2 < 502) #only looking at first 500ms, which is the blank screen

#we have 4 triplets, see each triplet max of 24 times, for a total of 96 triplets/288 imgs
#label each trial with which triplet they saw
#label each trial with the number of times they saw that triplet
hoo <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/blah_keep.csv")

#remove the 3 subs:
hoo<-hoo[!(hoo$id==2 |hoo$id==11 |hoo$id==38),]
hoo <- subset(hoo, TRIAL_INDEX > 1)
#average pupil size 
hoo2 <- ddply(famtrials2,.(sub,triplet_trialindex,image),summarise,meanpupil=mean(newpupil,na.rm = TRUE))
  
hoofinal <- cbind(hoo2,hoo)
hoofinal$sub <- NULL
hoofinal$TRIAL_INDEX <- NULL
hoofinal[,8] <- NULL

coo6 <- ddply(hoofinal,.(id,image,timesseen),summarise,meanpupil2=mean(meanpupil,na.rm = TRUE)) #collapse triplet id
coo7 <- ddply(coo6,.(image,timesseen),summarise,meanpupilSs=mean(meanpupil2,na.rm = TRUE),sepupil=sd(meanpupil2, na.rm = TRUE)/sqrt(length(meanpupil2))) #collapse across subjects

#plot
coo8 <- coo7

#cor.test
xyz1 <-cor.test(coo8$timesseen[coo8$image==1], coo8$meanpupilSs[coo8$image==1], alternative = "two.sided", method = "pearson")
xyz1
xyz2 <-cor.test(coo8$timesseen[coo8$image==2], coo8$meanpupilSs[coo8$image==2], alternative = "two.sided", method = "pearson")
xyz2
xyz3 <-cor.test(coo8$timesseen[coo8$image==3], coo8$meanpupilSs[coo8$image==3], alternative = "two.sided", method = "pearson")
xyz3

yoo3 <- data.frame(image= numeric(3), comments= numeric(3))
yoo3$image <- 1:3
yoo3$comments[1] <- "cor = -0.09, p = 0.6798"
yoo3$comments[2] <- "cor = 0.21, p = 0.3182"
yoo3$comments[3] <- "cor = 0.42, p = 0.04243"

famtrialsnames <- c(
                    `1` = "First in triplet",
                    `2` = "Second in triplet",
                    `3` = "Third in triplet"
                    )

ggplot(coo8,aes(x=timesseen,y=meanpupilSs,color=factor(image),fill=factor(image)))+geom_point()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_colour_manual(values=color.v1)+scale_fill_manual(values=color.v1)+
  ggtitle("Pupil change during anticipatory period (500ms) throughout experiment")+
  geom_text(data=yoo3, aes(x=12, y=0.09, label=comments), colour="black", size = 7)+
  labs(x = "Times seen triplet", y = "Change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+xlim(0, 24)+guides(color=FALSE)+facet_wrap(~image,labeller = as_labeller(famtrialsnames))+theme(strip.text = element_text(size=16))+stat_smooth(method=lm)+theme(legend.position="none")+scale_y_continuous(labels=percent,limits=c(-.05,.1),breaks=seq(-.05,.1,0.02))

```

times seen triplet for 750ms for new timecode, baselining everything to the first image in triplet
```{r}
famtrials2 <- subset(poo, TIMECODE2 > 500) #only looking at last 750, which is the pic

#we have 4 triplets, see each triplet max of 24 times, for a total of 96 triplets/288 imgs
#label each trial with which triplet they saw
#label each trial with the number of times they saw that triplet
hoo <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/blah_keep.csv")

#remove the 3 subs:
hoo<-hoo[!(hoo$id==2 |hoo$id==11 |hoo$id==38),]
hoo <- subset(hoo, TRIAL_INDEX > 1)
#average pupil size during 750ms
hoo2 <- ddply(famtrials2,.(sub,triplet_trialindex,image),summarise,meanpupil=mean(newpupil,na.rm = TRUE))
  
hoofinal <- cbind(hoo2,hoo)
hoofinal$sub <- NULL
hoofinal$TRIAL_INDEX <- NULL
hoofinal[,8] <- NULL

coo6 <- ddply(hoofinal,.(id,image,timesseen),summarise,meanpupil2=mean(meanpupil,na.rm = TRUE)) #collapse triplet id
coo7 <- ddply(coo6,.(image,timesseen),summarise,meanpupilSs=mean(meanpupil2,na.rm = TRUE),sepupil=sd(meanpupil2, na.rm = TRUE)/sqrt(length(meanpupil2))) #collapse across subjects

#above average
coo8 <- coo7

#cor.test
xyz1 <-cor.test(coo8$timesseen[coo8$image==1], coo8$meanpupilSs[coo8$image==1], alternative = "two.sided", method = "pearson")
xyz1
xyz2 <-cor.test(coo8$timesseen[coo8$image==2], coo8$meanpupilSs[coo8$image==2], alternative = "two.sided", method = "pearson")
xyz2
xyz3 <-cor.test(coo8$timesseen[coo8$image==3], coo8$meanpupilSs[coo8$image==3], alternative = "two.sided", method = "pearson")
xyz3

yoo3 <- data.frame(image= numeric(3), comments= numeric(3))
yoo3$image <- 1:3
yoo3$comments[1] <- "cor = 0.43, p = 0.03373*"
yoo3$comments[2] <- "cor = 0.52, p = 0.008958*"
yoo3$comments[3] <- "cor = 0.66, p = 0.0004609*"

famtrialsnames <- c(
                    `1` = "First in triplet",
                    `2` = "Second in triplet",
                    `3` = "Third in triplet"
                    )

ggplot(coo8,aes(x=timesseen,y=meanpupilSs,color=factor(image),fill=factor(image)))+geom_point()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_colour_manual(values=color.v1)+scale_fill_manual(values=color.v1)+
  ggtitle("Pupil change during viewing period (750ms) throughout experiment")+
  geom_text(data=yoo3, aes(x=12, y=0.09, label=comments), colour="black", size = 7)+
  labs(x = "Times seen triplet", y = "Change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+xlim(0, 24)+guides(color=FALSE)+facet_wrap(~image,labeller = as_labeller(famtrialsnames))+theme(strip.text = element_text(size=16))+stat_smooth(method=lm)+theme(legend.position="none")+scale_y_continuous(labels=percent,limits=c(-.05,.1),breaks=seq(-.05,.1,0.02))

```

breaking it down by accuracy

times seen triplet for 500ms X accuracy (above or below)
```{r}
boo1 <- subset(poo, TIMECODE2 < 502) #only looking at first 500ms, which is the blank screen

#ABOVE AVERAGE
boo_a <- subset(boo1, accuracy == 1)
  
#average pupil size 
boo2 <- ddply(boo_a,.(sub,image,timesseen),summarise,meanpupil2=mean(newpupil,na.rm = TRUE)) #collapse triplet id
boo3 <- ddply(boo2,.(image,timesseen),summarise,meanpupilSs=mean(meanpupil2,na.rm = TRUE),sepupil=sd(meanpupil2, na.rm = TRUE)/sqrt(length(meanpupil2))) #collapse across subjects
#remove first time seeing image 
boo3 <- subset(boo3, timesseen > 1)
#cor.test
xyz1 <-cor.test(boo3$timesseen[boo3$image==1], boo3$meanpupilSs[boo3$image==1], alternative = "two.sided", method = "pearson")
xyz1
xyz2 <-cor.test(boo3$timesseen[boo3$image==2], boo3$meanpupilSs[boo3$image==2], alternative = "two.sided", method = "pearson")
xyz2
xyz3 <-cor.test(boo3$timesseen[boo3$image==3], boo3$meanpupilSs[boo3$image==3], alternative = "two.sided", method = "pearson")
xyz3

yoo3 <- data.frame(image= numeric(3), comments= numeric(3))
yoo3$image <- 1:3
yoo3$comments[1] <- "cor = -0.17, p = 0.4231"
yoo3$comments[2] <- "cor = 0.25, p = 0.2439"
yoo3$comments[3] <- "cor = 0.16, p = 0.4615"

ggplot(boo3,aes(x=timesseen,y=meanpupilSs,color=factor(image),fill=factor(image)))+
  geom_point()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_colour_manual(values=color.v1)+scale_fill_manual(values=color.v1)+
  ggtitle("Pupil change during anticipatory period (500ms) (above average)")+
  labs(x = "Times seen triplet", y = "Change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+xlim(0, 24)+
  facet_wrap(~image)+theme(strip.text = element_text(size=16))+
  stat_smooth(method=lm)+theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(-0.1,.1),breaks=seq(-0.1,.1,0.02))+
  geom_text(data=yoo3, aes(x=15, y=-.08, label=comments), colour="black", size = 7)
  
#BELOW AVERAGE  
boo_b <- subset(boo1, accuracy == 0)
  
#average pupil size 
boo12 <- ddply(boo_b,.(sub,image,timesseen),summarise,meanpupil2=mean(newpupil,na.rm = TRUE)) #collapse triplet id
boo13 <- ddply(boo12,.(image,timesseen),summarise,meanpupilSs=mean(meanpupil2,na.rm = TRUE),sepupil=sd(meanpupil2, na.rm = TRUE)/sqrt(length(meanpupil2))) #collapse across subjects
#remove first time seeing image 
boo13 <- subset(boo13, timesseen > 1)
#cor.test
xyz1 <-cor.test(boo13$timesseen[boo13$image==1], boo13$meanpupilSs[boo3$image==1], alternative = "two.sided", method = "pearson")
xyz1
xyz2 <-cor.test(boo13$timesseen[boo13$image==2], boo13$meanpupilSs[boo3$image==2], alternative = "two.sided", method = "pearson")
xyz2
xyz3 <-cor.test(boo13$timesseen[boo13$image==3], boo13$meanpupilSs[boo3$image==3], alternative = "two.sided", method = "pearson")
xyz3

yoo3 <- data.frame(image= numeric(3), comments= numeric(3))
yoo3$image <- 1:3
yoo3$comments[1] <- "cor = 0.029, p = 0.8943"
yoo3$comments[2] <- "cor = -0.0006, p = 0.9976"
yoo3$comments[3] <- "cor = 0.235815, p = 0.2787"

ggplot(boo13,aes(x=timesseen,y=meanpupilSs,color=factor(image),fill=factor(image)))+
  geom_point()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_colour_manual(values=color.v1)+scale_fill_manual(values=color.v1)+
  ggtitle("Pupil change during anticipatory period (500ms) (below average)")+
  labs(x = "Times seen triplet", y = "Change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+xlim(0, 24)+
  facet_wrap(~image)+theme(strip.text = element_text(size=16))+
  stat_smooth(method=lm)+theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,0.1,0.02))+
  geom_text(data=yoo3, aes(x=15, y=-0.08, label=comments), colour="black", size = 7)

```

times seen triplet for 750ms for new timecode, baselining everything to the first image in triplet
```{r}
boo1 <- subset(poo, TIMECODE > 500 & TIMECODE < 1251) #only looking at last 750, which is the pic

#ABOVE AVERAGE
boo_a <- subset(boo1, accuracy == 1)
  
#average pupil size 
boo2 <- ddply(boo_a,.(sub,image,timesseen),summarise,meanpupil2=mean(newpupil,na.rm = TRUE)) #collapse triplet id
boo3 <- ddply(boo2,.(image,timesseen),summarise,meanpupilSs=mean(meanpupil2,na.rm = TRUE),sepupil=sd(meanpupil2, na.rm = TRUE)/sqrt(length(meanpupil2))) #collapse across subjects
#remove first time seeing image 
boo3 <- subset(boo3, timesseen > 1)
#cor.test
xyz1 <-cor.test(boo3$timesseen[boo3$image==1], boo3$meanpupilSs[boo3$image==1], alternative = "two.sided", method = "pearson")
xyz1
xyz2 <-cor.test(boo3$timesseen[boo3$image==2], boo3$meanpupilSs[boo3$image==2], alternative = "two.sided", method = "pearson")
xyz2
xyz3 <-cor.test(boo3$timesseen[boo3$image==3], boo3$meanpupilSs[boo3$image==3], alternative = "two.sided", method = "pearson")
xyz3

yoo3 <- data.frame(image= numeric(3), comments= numeric(3))
yoo3$image <- 1:3
yoo3$comments[1] <- "cor = 0.277, p = 0.1997"
yoo3$comments[2] <- "cor = 0.23, p = 0.2742"
yoo3$comments[3] <- "cor = 0.402, p = 0.056"

ggplot(boo3,aes(x=timesseen,y=meanpupilSs,color=factor(image),fill=factor(image)))+
  geom_point()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_colour_manual(values=color.v1)+scale_fill_manual(values=color.v1)+
  ggtitle("Pupil change during viewing period (750ms) (above average)")+
  labs(x = "Times seen triplet", y = "Change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+xlim(0, 24)+
  facet_wrap(~image)+theme(strip.text = element_text(size=16))+
  stat_smooth(method=lm)+theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(-0.1,.1),breaks=seq(-0.1,.1,0.02))+
  geom_text(data=yoo3, aes(x=15, y=-.08, label=comments), colour="black", size = 7)
  
#BELOW AVERAGE  
boo_b <- subset(boo1, accuracy == 0)
  
#average pupil size 
boo12 <- ddply(boo_b,.(sub,image,timesseen),summarise,meanpupil2=mean(newpupil,na.rm = TRUE)) #collapse triplet id
boo13 <- ddply(boo12,.(image,timesseen),summarise,meanpupilSs=mean(meanpupil2,na.rm = TRUE),sepupil=sd(meanpupil2, na.rm = TRUE)/sqrt(length(meanpupil2))) #collapse across subjects
#remove first time seeing image 
boo13 <- subset(boo13, timesseen > 1)
#cor.test
xyz1 <-cor.test(boo13$timesseen[boo13$image==1], boo13$meanpupilSs[boo3$image==1], alternative = "two.sided", method = "pearson")
xyz1
xyz2 <-cor.test(boo13$timesseen[boo13$image==2], boo13$meanpupilSs[boo3$image==2], alternative = "two.sided", method = "pearson")
xyz2
xyz3 <-cor.test(boo13$timesseen[boo13$image==3], boo13$meanpupilSs[boo3$image==3], alternative = "two.sided", method = "pearson")
xyz3

yoo3 <- data.frame(image= numeric(3), comments= numeric(3))
yoo3$image <- 1:3
yoo3$comments[1] <- "cor = 0.58, p = 0.003604"
yoo3$comments[2] <- "cor = 0.209, p = 0.337"
yoo3$comments[3] <- "cor = 0.32, p = 0.1363"

ggplot(boo13,aes(x=timesseen,y=meanpupilSs,color=factor(image),fill=factor(image)))+
  geom_point()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_colour_manual(values=color.v1)+scale_fill_manual(values=color.v1)+
  ggtitle("Pupil change during viewing period (750ms) (below average)")+
  labs(x = "Times seen triplet", y = "Change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+xlim(0, 24)+
  facet_wrap(~image)+theme(strip.text = element_text(size=16))+
  stat_smooth(method=lm)+theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,0.1,0.02))+
  geom_text(data=yoo3, aes(x=15, y=-0.08, label=comments), colour="black", size = 7)

```
