---
title: "Jan 30 2018"
author: "Felicia Zhang"
date: '2018-01-30'
output: html_document
---


Recreating graphs for VSL paper
Making sure graphs are consistent with labels, colors
```{r setup, include=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)
library(tidyr)

#1. load data (master)
OV1Orig = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/OV1_zscore.rds") 
OmixOrig = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges_Mix/Data/Omix_zscore.rds")
Omix.Trip = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges_Mix/Data/Omix_trip_zscore.rds")
Omix.Rand = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges_Mix/Data/Omix_rand_zscore.rds")

#O_V1:
#pupil corrected = pupil change from baseline
#image = triplet position (1, 2 or 3)
#newtime = time for each image in triplet (0-1250ms)
#triplet = which triplet it is (1, 2, 3 or 4)
#sub = faster way to index subjects
#triplet_trialindex = trial number based on triplet (range 1 - 96)
#timesseen = times seen the triplet (range 1- 24)
#accuracy = coding if subject scored above or below the average accuracy (0 = below, 1 = above)
#newtime2 = time for each triplet (0-3750ms)
#newtime3 = recode time: 500ms, and then 750ms (0-1250ms)
#timecode2 = recode time: 500ms, and then 750ms (0-1250ms)
#timecode3 = time for each triplet (0-3750ms)

#OMix:
#pupil corrected = baseline is each image
#pupil corrected 2 = baseline first image of triplet
#block = 1 = triplet, 2 = random
#imageseq = first, second or third image in triplet
#timesseen = times seen the triplet (range 1- 20)
#TRIP_TRIAL_INDEX = correct triplet trial number
#TIMECODE2 = correct 0 - 3754ms

#save Z-score dataframes
#saveRDS(poo, file="OV1_zscore.rds")
#saveRDS(poo.mix, file="Omix_zscore.rds")
#saveRDS(poo.rand, file="Omix_rand_zscore.rds")
#saveRDS(poo.trip, file="Omix_trip_zscore.rds")
```

Setting color palettes
```{r}
#colors
color.t <- c("#FFCC00", "#ff9900","#FF6600")
color.a <- c("#FFCC00", "#ff9900") 
color.aa <- c("#bacfe3", "#2875be")  #blue
color.ba <- c("#f15e6a", "#9c2b35")  #red
color.trip <- c("#c9e29f","#58a329","#327508")  #triplet green
color.ran <- c("#ddcfe8", "#7c60c3","#481f9d")  #random purple
```

Correct baseline pupil size using Brisson et al. (2013) paper
```{r}
#remove NAs
OV1 <- OV1Orig %>% drop_na(RIGHT_GAZE_X)
OV1 <- OV1 %>% drop_na(RIGHT_GAZE_Y)

#run model
model1 <- lm(RIGHT_PUPIL_SIZE ~ RIGHT_GAZE_X + RIGHT_GAZE_Y, data = OV1)

#residual = correct pupil size
OV1$CORRECT_RAW_PUPIL <- resid(model1)

#result = must have X and Y coordinates, but for babies we didn't collect Y coordinates. 
```

Oranges V1 Graphs
```{r}
a1 <- OV1Orig

#histogram of accuracy
OV1accuracy = read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Oranges/Data/Oranges_accuracy.csv")
OV1accuracy<-OV1accuracy[!(OV1accuracy$subject==2 |OV1accuracy$subject==11|OV1accuracy$subject==33 |OV1accuracy$subject==38),] #remove bad subjects
c <- mean(OV1accuracy$accuracy)

ggplot(OV1accuracy,aes(OV1accuracy$accuracy))+geom_histogram()+
  scale_y_continuous(limits=c(0,10),breaks=seq(0,10,1))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Histogram of accuracy")+
  labs(x = "Accuracy (%)", y = "Number of participants")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_x_continuous(label=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  geom_vline(xintercept = c, linetype = "longdash", color="red",size = 1)+
  theme(plot.title = element_text(hjust = 0.5))

#timecourse
a=c(500, 1750, 3000)
b=c(1250,2500)

a2 <- ddply(a1,.(RECORDING_SESSION_LABEL,TIMECODE3),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #collapse across subjects
a3 <- ddply(a2,.(TIMECODE3),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

ggplot(a3,aes(x=TIMECODE3,y=meanPUPILSs))+geom_line()+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,0.02))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Pupil change during triplet")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_vline(xintercept = b, size = 1.5)+
  geom_vline(xintercept = a, linetype = "longdash")+
  scale_x_continuous(limits=c(0,3750),breaks=seq(0,3750,500), expand = c(0, 0))+
  scale_fill_manual(values=color.t)+scale_colour_manual(values=color.t)

#timecourse overlay
b1 <- ddply(a1,.(RECORDING_SESSION_LABEL,image,TIMECODE2),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #collapse across subjects
b2 <- ddply(b1,.(image,TIMECODE2),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

ggplot(b2,aes(x=TIMECODE2,y=meanPUPILSs,color=factor(image),fill=factor(image)))+geom_line()+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,0.02))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_vline(xintercept = 500, linetype = "longdash")+
  scale_x_continuous(limits=c(0,1250), breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_fill_manual(values=color.t, name="Image",breaks=c("1", "2","3"),labels=c("1", "2","3"))+
  guides(color=FALSE)+
  scale_colour_manual(values=color.t)+
  theme(plot.title = element_text(hjust = 0.5))

#triplet timecourse, for accuracy
c1 <- ddply(a1,.(RECORDING_SESSION_LABEL,accuracy,TIMECODE3),summarise,meanPUPIL=mean(newpupil,na.rm = TRUE)) #collapse across subjects
c2 <- ddply(c1,.(accuracy,TIMECODE3),summarise,meanPUPILSs=mean(meanPUPIL,na.rm = TRUE),sePUPIL=sd(meanPUPIL, na.rm = TRUE)/sqrt(length(meanPUPIL))) #collapse across subjects

ggplot(c2,aes(x=TIMECODE3,y=meanPUPILSs,color=factor(accuracy),fill=factor(accuracy)))+
  geom_line()+
  geom_ribbon(aes(ymin=meanPUPILSs-sePUPIL,ymax=meanPUPILSs+sePUPIL),alpha=0.4)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,0.02))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("Pupil change during triplet")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_vline(xintercept = b, size = 1.5)+
  geom_vline(xintercept = a, linetype = "longdash")+
  scale_x_continuous(limits=c(0,3750),breaks=seq(0,3750,500), expand = c(0, 0))+
  scale_fill_brewer(palette="Set1",name="Accuracy",breaks=c("0", "1"),labels=c("below average", "above average"))+guides(color=FALSE)+
  scale_colour_brewer(palette="Set1")+
  theme(legend.position = "bottom")

```

Oranges V1 Analyses: Accuracy
```{r}
#ACCURACY
#The average accuracy score on the test phase was 60% which is above chance (50%) (need to check if 60% is stat sig above 50%). 
OV1accuracy<-OV1accuracy[!(OV1accuracy$subject==2 |OV1accuracy$subject==11|OV1accuracy$subject==33 |OV1accuracy$subject==38),] #remove bad subjects

res <- t.test(OV1accuracy$accuracy, mu = 0.5)
res
#t = 5.23, p-value < 0.001
```

Oranges V1: correlation pupil response and accuracy
```{r}
#entire trial
foo <- group_by(OV1Orig, sub, accuracy2) %>%
  summarise(
    pupilavg=mean(newpupil,na.rm = TRUE)
    )
foo$trial <- 1

#anticipatory period
famtrials3 <- subset(OV1Orig, TIMECODE2 < 502) 
foo2 <- group_by(famtrials3, sub, accuracy2) %>%
  summarise(
    pupilavg=mean(newpupil,na.rm = TRUE)
    )
foo2$trial <- 2
#viewing period
famtrials3 <- subset(OV1Orig, TIMECODE2 > 500)
foo3 <- group_by(famtrials3, sub, accuracy2) %>%
  summarise(
    pupilavg=mean(newpupil,na.rm = TRUE)
    )
foo3$trial <- 3

foofinal <- rbind(foo, foo2, foo3)

split <- c(`1` = "Entire trial",`2` = "Anticipatory period",`3` = "Viewing period")

ggplot(foofinal,aes(x=accuracy2,y=pupilavg))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "Accuracy (%)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent)+
  scale_x_continuous(labels=percent)+
  facet_wrap(~trial,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=14))+
  geom_smooth(method="lm", se = FALSE)
```

Oranges V1 Analyses: Regression
pupil change ~ accuracy + image + times seen
```{r}
#add in continuous accuracy variable
OV1Orig$accuracy2 <- 0

sub <- unique(OV1Orig$sub)
for (i in 1:length(sub)) {
  OV1Orig$accuracy2[OV1Orig$sub==sub[i]] <- OV1accuracy$accuracy[i]
}

#anticipatory period: 500ms
famtrials3 <- subset(OV1Orig, TIMECODE2 < 502)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model500 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ image + (1|sub), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit2 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model500) 

fit3 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model500) #(1|sub = intercept)

anova(fit1,fit2,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 0.026

summary(fit3) #image + accuracy + timesseen + (1 | sub)
#within a trial, pupil size increases for image seen p = 3.91e-06***
#throughout the experiment, size increases p = 0.0263*
#no diff in accuracy :( p = 0.2835

#add interaction
fit4 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model500) #(1|sub = intercept)
summary(fit4)
#nothing

#750ms
famtrials3 <- subset(OV1Orig, TIMECODE2 > 500)

#participant (1-53), triplet presentation (1-24), image position (1-3), overall position in the stream (1-288), accuracy
model750 <- ddply(famtrials3,.(sub,timesseen,image,triplet_trialindex,accuracy2),summarise,meanpupil=mean(newpupil,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ image + (1|sub), data = model750)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |sub), data = model500) #can also include accuracy as continuous
fit21 <- lmer(meanpupil ~ image + accuracy2 + (1|sub), data = model750) 

fit31 <- lmer(meanpupil ~ image + accuracy2 + timesseen + (1|sub), data = model750) #(1|sub = intercept)

anova(fit11,fit21,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#including timesseen and accuracy helped a lot p = 1.9e-07***

summary(fit31) #image + accuracy + timesseen + (1 | sub)
#within a trial, no pupil size increases for image seen
#throughout the experiment, size increases timesseen p = 1.93e-07
#no diff in accuracy :(

#add interaction
fit41 <- lmer(meanpupil ~ image * accuracy2 * timesseen + (1|sub), data = model750) #(1|sub = intercept)
summary(fit41)
#nothing

```

Oranges Mix Graphs
```{r}
#only keep center looks
orig2 <- OmixOrig
a <- which(orig2$RIGHT_GAZE_X < 440)
orig2 <- orig2[-c(a), ]
a <- which(orig2$RIGHT_GAZE_Y < 312)
orig2 <- orig2[-c(a), ]
a <- which(orig2$RIGHT_GAZE_X > 840)
orig2 <- orig2[-c(a), ]
a <- which(orig2$RIGHT_GAZE_Y > 712)
orig2 <- orig2[-c(a), ]

block1 <- subset(orig2, TRIAL_INDEX < 241)
block2 <- subset(orig2, TRIAL_INDEX > 240)

###Timecourse
#block 1 overlay
d1 <- ddply(block1,.(subID,TIMECODE,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
d2 <- ddply(d1,.(TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(d2,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,.02))+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Triplet block")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.trip)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_color_manual(values=color.trip)+
  theme(plot.title = element_text(hjust = 0.5))

#block 2 overlay
goo <- ddply(block2,.(subID,TIMECODE,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
goo2 <- ddply(goo,.(TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(goo2,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,.02))+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Random block")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.ran)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_colour_manual(values=color.ran)+
  theme(plot.title = element_text(hjust = 0.5))

#timecourse block 1 + block 2 overlay

coo1 <- ddply(block1,.(subID,TIMECODE2),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
coo2 <- ddply(block2,.(subID,TIMECODE2),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE))
coo1$block <- 1
coo2$block <- 2
coo3 <- ddply(coo1,.(TIMECODE2,block),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))
coo4 <- ddply(coo2,.(TIMECODE2,block),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

a = c(500,1750,3000)
aa = c(1250,2500)

coo5 <- rbind(coo3,coo4)

ggplot(coo5,aes(x=TIMECODE2,y=meanPUPIL,color=factor(block),fill=factor(block)))+geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+ggtitle("Timecourse")+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.4)+
  scale_x_continuous(limits=c(0,3754),breaks=seq(0,3754,500), expand = c(0, 0))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(-.1,.1),breaks=seq(-.1,.1,.02))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Accent",name="Block",breaks=c("1","2"),labels=c("Triplet", "Random"))+
  scale_color_brewer(palette="Accent")+
  theme(legend.position = "bottom")+
  geom_vline(xintercept = a, linetype = "longdash")+
  geom_vline(xintercept = aa, size =1)
```

Oranges Mix Analyses: Regression
pupil change ~ image + times seen 
anticipatory period: 500ms
```{r}
#triplet block
famtrials3 <- subset(Omix.Trip, TIMECODE < 502)

#participant (1-53), timesseen (1-24), image position (1-3), block (0,1), accuracy
model500 <- ddply(famtrials3,.(subID,timesseen,imageseq,block),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 
model500$block <- model500$block-1

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ imageseq + (1|subID), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |subID), data = model500) #can also include accuracy as continuous

fit3 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model500) #(1|sub = intercept)

anova(fit1,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit3 is better
summary(fit3)
#Result: image seq is significant (B= 0.005316, p = 0.0002) and familiarity effect (B=0.0006058, p=0.0028)

#add interaction
fit4 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model500) #(1|sub = intercept)
summary(fit4)
#sig interaction for imageseq:timessseen p = 0.0375

#random block
famtrials3 <- subset(Omix.Rand, TIMECODE < 502)

#fill in timesseen
famtrials3$timesseen[famtrials3$TRIAL_INDEX < 253] <- 1
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 252 & famtrials3$TRIAL_INDEX < 265] <- 2
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 264 & famtrials3$TRIAL_INDEX < 277] <- 3
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 276 & famtrials3$TRIAL_INDEX < 289] <- 4
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 288 & famtrials3$TRIAL_INDEX < 301] <- 5
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 300 & famtrials3$TRIAL_INDEX < 313] <- 6
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 312 & famtrials3$TRIAL_INDEX < 325] <- 7
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 324 & famtrials3$TRIAL_INDEX < 337] <- 8
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 336 & famtrials3$TRIAL_INDEX < 349] <- 9
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 348 & famtrials3$TRIAL_INDEX < 361] <- 10
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 360 & famtrials3$TRIAL_INDEX < 373] <- 11
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 372 & famtrials3$TRIAL_INDEX < 385] <- 12
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 384 & famtrials3$TRIAL_INDEX < 397] <- 13
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 396 & famtrials3$TRIAL_INDEX < 409] <- 14
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 408 & famtrials3$TRIAL_INDEX < 421] <- 15
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 420 & famtrials3$TRIAL_INDEX < 433] <- 16
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 432 & famtrials3$TRIAL_INDEX < 445] <- 17
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 444 & famtrials3$TRIAL_INDEX < 457] <- 18
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 456 & famtrials3$TRIAL_INDEX < 469] <- 19
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 468] <- 20

#participant (1-53), timesseen (1-24), image position (1-3), block (0,1), accuracy
model500 <- ddply(famtrials3,.(subID,timesseen,imageseq,block),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 

#create nested models to help you pick 
fit1 <- lmer(meanpupil ~ imageseq + (1|subID), data = model500)

#fit2 <- lmer(meanpupil ~ image + factor(accuracy) + (1 |subID), data = model500) #can also include accuracy as continuous

fit3 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model500) #(1|sub = intercept)

anova(fit1,fit3)
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit1 and fit3 are the same
summary(fit3)
#image seq is significant (B= 0.009396, p = 0.0176) even for random it gets larger which goes against our hypothesis

#add interaction
fit4 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model500) #(1|sub = intercept)
summary(fit4)
#nothing
```

Oranges Mix Analyses: Regression
pupil change ~ image + times seen 
viewing period: 750ms
```{r}
#triplet block
famtrials3 <- subset(Omix.Trip, TIMECODE > 500)

#participant (1-53), triplet presentation (1-24), image position (1-3)
model750 <- ddply(famtrials3,.(subID,timesseen,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ imageseq + (1|subID), data = model750)

fit31 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model750) #(1|sub = intercept)

anova(fit11,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit31 is better

summary(fit31) 
#Result: familiarity effect size increases timesseen (B=0.0007522, p = 0.00126)

#add interaction
fit41 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model750) #(1|sub = intercept)
summary(fit41)
#sig interaction for imageseq:timessseen p = 0.04

#random block
famtrials3 <- subset(Omix.Rand, TIMECODE > 500)

#fill in timesseen
famtrials3$timesseen[famtrials3$TRIAL_INDEX < 253] <- 1
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 252 & famtrials3$TRIAL_INDEX < 265] <- 2
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 264 & famtrials3$TRIAL_INDEX < 277] <- 3
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 276 & famtrials3$TRIAL_INDEX < 289] <- 4
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 288 & famtrials3$TRIAL_INDEX < 301] <- 5
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 300 & famtrials3$TRIAL_INDEX < 313] <- 6
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 312 & famtrials3$TRIAL_INDEX < 325] <- 7
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 324 & famtrials3$TRIAL_INDEX < 337] <- 8
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 336 & famtrials3$TRIAL_INDEX < 349] <- 9
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 348 & famtrials3$TRIAL_INDEX < 361] <- 10
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 360 & famtrials3$TRIAL_INDEX < 373] <- 11
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 372 & famtrials3$TRIAL_INDEX < 385] <- 12
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 384 & famtrials3$TRIAL_INDEX < 397] <- 13
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 396 & famtrials3$TRIAL_INDEX < 409] <- 14
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 408 & famtrials3$TRIAL_INDEX < 421] <- 15
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 420 & famtrials3$TRIAL_INDEX < 433] <- 16
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 432 & famtrials3$TRIAL_INDEX < 445] <- 17
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 444 & famtrials3$TRIAL_INDEX < 457] <- 18
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 456 & famtrials3$TRIAL_INDEX < 469] <- 19
famtrials3$timesseen[famtrials3$TRIAL_INDEX > 468] <- 20

#participant (1-53), triplet presentation (1-24), image position (1-3)
model750 <- ddply(famtrials3,.(subID,timesseen,imageseq),summarise,meanpupil=mean(PUPIL_CORRECTED_2,na.rm = TRUE)) 

#create nested models to help you pick 
fit11 <- lmer(meanpupil ~ imageseq + (1|subID), data = model750)

fit31 <- lmer(meanpupil ~ imageseq + timesseen + (1|subID), data = model750) #(1|sub = intercept)

anova(fit11,fit31)
#comparing it to fit1
#anova measures difference for residual sum of squares (RSS) is a statistical technique used to measure the amount of variance in a data set that is not explained by the regression model
#fit11 and fit31 are the same

summary(fit31) 
#Result: nothing

#add interaction
fit41 <- lmer(meanpupil ~ imageseq * timesseen + (1|subID), data = model750) #(1|sub = intercept)
summary(fit41)
#nothing

```

Z-score: Oranges V1
```{r}
####################################################
################ Z-SCORE PER SUBJECT ############### 
####################################################
poo <- OV1Orig
subs <- unique(poo$sub)
poo$zscore <- 1

for (j in 1:length(subs)) {
  #for each subject
  v1 <- subset(poo, sub==subs[j])  
  sub_sd <- sd(v1$RIGHT_PUPIL_SIZE, na.rm = TRUE)* sqrt((length(v1$RIGHT_PUPIL_SIZE)-1)/(length(v1$RIGHT_PUPIL_SIZE)))
  sub_mean <- mean(v1$RIGHT_PUPIL_SIZE,na.rm = TRUE)
  
  #z-score calculation
  x <- min(which(poo$sub==subs[j]))
  xx <- max(which(poo$sub==subs[j]))
  poo$zscore[x:xx] <- (v1$RIGHT_PUPIL_SIZE - sub_mean)/sub_sd
  print(j)
}

###################### GRAPHS ###################### 

#timecourse
coo <- ddply(poo,.(sub,TIMECODE2,image),summarise,meanpupil=mean(zscore,na.rm = TRUE))
coo2 <- ddply(coo,.(TIMECODE2,image),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(coo2,aes(x=TIMECODE2,y=meanPUPIL,color=factor(image),fill=factor(image)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesV1: Z-score subject")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")

####################################################
################ Z-SCORE PER TRIPLET TRIAL #########
####################################################

#Z-score per triplet
poo$zscore.trip.trial <- 1
subs <- unique(poo$sub)

for (j in 1:length(subs)) {
  trials <- unique(poo$triplet_trialindex[poo$sub==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #for each triplet trial
    sub_sd <- sd(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$triplet_trialindex==trials[i]],na.rm = TRUE)*sqrt((length(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$triplet_trialindex==trials[i]])-1) /(length(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$triplet_trialindex==trials[i]])))
    sub_mean <- mean(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$triplet_trialindex==trials[i]], na.rm = TRUE)
    #z-score calculation
    poo$zscore.trip.trial[poo$triplet_trialindex == trials[i] & poo$sub == subs[j]] <- (poo$RIGHT_PUPIL_SIZE[poo$triplet_trialindex == trials[i] & poo$sub == subs[j]] - sub_mean)/sub_sd
  }}

###################### GRAPHS ######################  
doo <- ddply(poo,.(sub,TIMECODE2,image),summarise,meanpupil=mean(zscore.trip.trial,na.rm = TRUE))
doo2 <- ddply(doo,.(TIMECODE2,image),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(doo2,aes(x=TIMECODE2,y=meanPUPIL,color=factor(image),fill=factor(image)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesV1: Z-score triplet trial")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")

#average PDR bar graph
poo <- OV1Orig  
poo$period <- 1
poo$period[poo$TIMECODE2 > 500] <- 2
coo <- ddply(poo,.(sub,period,image),summarise,meanpupil=mean(zscore.trip.trial,na.rm = TRUE))
coo2 <- ddply(coo,.(period,image),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))
limits <- aes(ymax = meanPUPIL + sePUPIL, ymin=meanPUPIL - sePUPIL)
split <- c(`1` = "anticipatory",`2` = "viewing")

ggplot(coo2,aes(x=image,y=meanPUPIL,color=factor(image),fill=factor(image)))+
  geom_bar(stat="identity")+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesV1: Z-score subject")+
  labs(x = "Position in triplet", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  scale_color_manual(values=color.t)+
  scale_y_continuous(limits=c(-0.4,.2),breaks=seq(-0.4,.2,.05))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")+
  facet_wrap(~period,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")

####################################################
################ Z-SCORE PER TRIAL ################# 
####################################################

#Z-score per trial
poo$zscore.trial <- 1
subs <- unique(poo$sub)

for (j in 1:length(subs)) {
  trials <- unique(poo$TRIAL_INDEX[poo$sub==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #for each triplet trial
    sub_sd <- sd(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$TRIAL_INDEX==trials[i]],na.rm = TRUE)*sqrt((length(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$TRIAL_INDEX==trials[i]])-1) /(length(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$TRIAL_INDEX==trials[i]])))
    sub_mean <- mean(poo$RIGHT_PUPIL_SIZE[poo$sub==subs[j] & poo$TRIAL_INDEX==trials[i]], na.rm = TRUE)
    #z-score calculation
    poo$zscore.trial[poo$TRIAL_INDEX == trials[i] & poo$sub == subs[j]] <- (poo$RIGHT_PUPIL_SIZE[poo$TRIAL_INDEX == trials[i] & poo$sub == subs[j]] - sub_mean)/sub_sd
  }}

###################### GRAPHS ######################  
foo <- ddply(poo,.(sub,TIMECODE2,image),summarise,meanpupil=mean(zscore.trial,na.rm = TRUE))
foo2 <- ddply(foo,.(TIMECODE2,image),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(foo2,aes(x=TIMECODE2,y=meanPUPIL,color=factor(image),fill=factor(image)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesV1: Z-score trial")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")  

```

Z-score: OMix
````{r}
####################################################
############## Z-SCORE PER SUBJECT #################
####################################################
poo.mix <- OmixOrig
subs <- unique(poo.mix$subID)
poo.mix$zscore.sub <- 1

for (j in 1:length(subs)) {
  #for each subject
  v1 <- subset(poo.mix, subID==subs[j])  
  sub_sd <- sd(v1$RIGHT_PUPIL_SIZE, na.rm = TRUE)* sqrt((length(v1$RIGHT_PUPIL_SIZE)-1)/(length(v1$RIGHT_PUPIL_SIZE)))
  sub_mean <- mean(v1$RIGHT_PUPIL_SIZE,na.rm = TRUE)
  
  #z-score calculation
  x <- min(which(poo.mix$subID==subs[j]))
  xx <- max(which(poo.mix$subID==subs[j]))
  poo.mix$zscore.sub[x:xx] <- (v1$RIGHT_PUPIL_SIZE - sub_mean)/sub_sd
  print(j)
}

###################### GRAPHS ###################### 

coo <- ddply(poo.mix,.(subID,block,TIMECODE,imageseq),summarise,meanpupil=mean(zscore.sub,na.rm = TRUE))
coo2 <- ddply(coo,.(block,TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))
coo3 <- subset(coo2, block==1) #triplet block

ggplot(coo3,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesMix: Z-score triplet block")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")  

coo4 <- subset(coo2, block==2) #random block

ggplot(coo4,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesMix: Z-score random block")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")  

####################################################
################ Z-SCORE PER BLOCK #################
####################################################
subs <- unique(poo.mix$subID)
poo.mix$zscore.block <- 1

for (j in 1:length(subs)) {
  blocks <- unique(poo.mix$block[poo.mix$subID==subs[j]])
  print(j)
  for (i in 1:length(blocks)) {
    #for each block
    sub_sd <- sd(poo.mix$RIGHT_PUPIL_SIZE[poo.mix$subID==subs[j] & poo.mix$block==blocks[i]],na.rm = TRUE)*sqrt((length(poo.mix$RIGHT_PUPIL_SIZE[poo.mix$subID==subs[j] & poo.mix$block==blocks[i]])-1) /(length(poo.mix$RIGHT_PUPIL_SIZE[poo.mix$subID==subs[j] & poo.mix$block==blocks[i]])))
    sub_mean <- mean(poo.mix$RIGHT_PUPIL_SIZE[poo.mix$subID==subs[j] & poo.mix$block==blocks[i]], na.rm = TRUE)
    
    #z-score calculation
    poo.mix$zscore.block[poo.mix$block == blocks[i] & poo.mix$subID == subs[j]] <- (poo.mix$RIGHT_PUPIL_SIZE[poo.mix$block == blocks[i] & poo.mix$subID == subs[j]] - sub_mean)/sub_sd
  }}

###################### GRAPHS ###################### 

coo <- ddply(poo.mix,.(subID,block,TIMECODE,imageseq),summarise,meanpupil=mean(zscore.block,na.rm = TRUE))
coo2 <- ddply(coo,.(block,TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))
coo3 <- subset(coo2, block==1) #triplet block

ggplot(coo3,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesMix: Z-score triplet block")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")  

coo4 <- subset(coo2, block==2) #random block

ggplot(coo4,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesMix: Z-score random block")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")  

####################################################
################ Z-SCORE PER TRIPLET TRIAL #########
####################################################

#Z-score triplet block
poo.trip <- subset(poo.mix, block==1)
poo.trip$zscore.trip.trial <- 1
subs <- unique(poo.trip$subID)

for (j in 1:length(subs)) {
  trials <- unique(poo.trip$TRIP_TRIAL_INDEX[poo.trip$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #for each triplet trial
    sub_sd <- sd(poo.trip$RIGHT_PUPIL_SIZE[poo.trip$subID==subs[j] & poo.trip$TRIP_TRIAL_INDEX==trials[i]],na.rm = TRUE)*sqrt((length(poo.trip$RIGHT_PUPIL_SIZE[poo.trip$subID==subs[j] & poo.trip$TRIP_TRIAL_INDEX==trials[i]])-1) /(length(poo.trip$RIGHT_PUPIL_SIZE[poo.trip$subID==subs[j] & poo.trip$TRIP_TRIAL_INDEX==trials[i]])))
    sub_mean <- mean(poo.trip$RIGHT_PUPIL_SIZE[poo.trip$subID==subs[j] & poo.trip$TRIP_TRIAL_INDEX==trials[i]], na.rm = TRUE)
    
    #z-score calculation
    poo.trip$zscore.trip.trial[poo.trip$TRIP_TRIAL_INDEX == trials[i] & poo.trip$subID == subs[j]] <- (poo.trip$RIGHT_PUPIL_SIZE[poo.trip$TRIP_TRIAL_INDEX == trials[i] & poo.trip$subID == subs[j]] - sub_mean)/sub_sd
  }}

#z-score random block
poo.rand <- subset(poo.mix, block==2)
poo.rand$zscore.trip.trial <- 1
subs <- unique(poo.rand$subID)

for (j in 1:length(subs)) {
  trials <- unique(poo.rand$TRIP_TRIAL_INDEX[poo.rand$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #for each triplet trial
    sub_sd <- sd(poo.rand$RIGHT_PUPIL_SIZE[poo.rand$subID==subs[j] & poo.rand$TRIP_TRIAL_INDEX==trials[i]],na.rm = TRUE)*sqrt((length(poo.rand$RIGHT_PUPIL_SIZE[poo.rand$subID==subs[j] & poo.rand$TRIP_TRIAL_INDEX==trials[i]])-1) /(length(poo.rand$RIGHT_PUPIL_SIZE[poo.rand$subID==subs[j] & poo.rand$TRIP_TRIAL_INDEX==trials[i]])))
    sub_mean <- mean(poo.rand$RIGHT_PUPIL_SIZE[poo.rand$subID==subs[j] & poo.rand$TRIP_TRIAL_INDEX==trials[i]], na.rm = TRUE)
    
    #z-score calculation
    poo.rand$zscore.trip.trial[poo.rand$TRIP_TRIAL_INDEX == trials[i] & poo.rand$subID == subs[j]] <- (poo.rand$RIGHT_PUPIL_SIZE[poo.rand$TRIP_TRIAL_INDEX == trials[i] & poo.rand$subID == subs[j]] - sub_mean)/sub_sd
  }}

###################### GRAPHS ######################  
coo <- ddply(poo.trip,.(subID,TIMECODE,imageseq),summarise,meanpupil=mean(zscore.trip.trial,na.rm = TRUE))
coo2 <- ddply(coo,.(TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(coo2,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesMix: Z-score triplet block")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")  

#random block
coo3 <- ddply(poo.rand,.(subID,TIMECODE,imageseq),summarise,meanpupil=mean(zscore.trip.trial,na.rm = TRUE))
coo4 <- ddply(coo3,.(TIMECODE,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))

ggplot(coo4,aes(x=TIMECODE,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_line()+
  scale_x_continuous(limits=c(0,1250),breaks=seq(0,1250,200), expand = c(0, 0))+
  scale_colour_manual(values=color.t)+
  geom_ribbon(aes(ymin=meanPUPIL-sePUPIL,ymax=meanPUPIL+sePUPIL),alpha=0.3)+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OrangesMix: Z-score random block")+
  labs(x = "Time (ms)", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  geom_vline(xintercept = 500,linetype = "longdash")+
  scale_y_continuous(limits=c(-0.5,.5),breaks=seq(-0.5,.5,.1))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")  

#average PDR bar graph Triplet Block
foo <- Omix.Trip  
foo$period <- 1
foo$period[foo$TIMECODE > 500] <- 2
foo2 <- ddply(foo,.(subID,period,imageseq),summarise,meanpupil=mean(zscore.trip.trial,na.rm = TRUE))
foo3 <- ddply(foo2,.(period,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))
limits <- aes(ymax = meanPUPIL + sePUPIL, ymin=meanPUPIL - sePUPIL)
split <- c(`1` = "anticipatory",`2` = "viewing")

ggplot(foo3,aes(x=imageseq,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_bar(stat="identity")+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OMix Triplet Block")+
  labs(x = "Position in triplet", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  scale_color_manual(values=color.t)+
  scale_y_continuous(limits=c(-0.4,.2),breaks=seq(-0.4,.2,.05))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")+
  facet_wrap(~period,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")

#average PDR bar graph Random Block
foo <- Omix.Rand
foo$period <- 1
foo$period[foo$TIMECODE > 500] <- 2
foo2 <- ddply(foo,.(subID,period,imageseq),summarise,meanpupil=mean(zscore.trip.trial,na.rm = TRUE))
foo3 <- ddply(foo2,.(period,imageseq),summarise,meanPUPIL=mean(meanpupil,na.rm = TRUE),sePUPIL=sd(meanpupil, na.rm = TRUE)/sqrt(length(meanpupil)))
limits <- aes(ymax = meanPUPIL + sePUPIL, ymin=meanPUPIL - sePUPIL)
split <- c(`1` = "anticipatory",`2` = "viewing")

ggplot(foo3,aes(x=imageseq,y=meanPUPIL,color=factor(imageseq),fill=factor(imageseq)))+
  geom_bar(stat="identity")+
  guides(color=FALSE)+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("OMix Random Block")+
  labs(x = "Position in triplet", y = "Pupil dilation (z-score)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  scale_fill_manual(name="Image",values=color.t)+
  scale_color_manual(values=color.t)+
  scale_y_continuous(limits=c(-0.4,.2),breaks=seq(-0.4,.2,.05))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "bottom")+
  facet_wrap(~period,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  geom_errorbar(limits, width=0.25,color="black")
```